%!TEX root = ../Main.tex

\chapter{PolyMarker: A fast polyploid primer design pipeline}


\subsection{Manual process of primer design(Introduction)} 
Explain how the SNP markers are designed without the tool. 

\subsection{Global alignment} 
Search of the contigs with the sequence in the CSS reference and the importance of being able to distinguish between homoeologous regions. 

\subsection{Local alignment} 
Once the region with the primer has been selected, make a local alignment. This section discusses why the local alignment is needed. 

\subsection{Primer design tools} 
In this section, the principles of \textit{in silico} primer design are discussed, and why not simply selecting a genomic variation is enough (thermal stability, primers folding on themselves)

\subsection{Primer selection algorithms} 
Different algorithms to select the \"best primer\". 

\subsubsection{Regular markers}  
Algorithm to select the two primers with a geneome-specific variation. For amplicons/capillary sequencing. 

\subsubsection{KASP markers} 
For KASP markers, the product should be as short as possible with the mutation in the first three bases. 

\subsubsection{Deletion algorithms}
Algorithm to produce KASP for deletions in polyploids. 

\subsection{Designed markers} Details of the generated primers for the 80k iSelect chip and the 820k axiom chip. This section also include counts on how many are genome specific, semi-specific and non specific. Also an analysis of how many are repeated or map to more than one chromosome perfectly.

\subsection{Conclusions} Remarks on the importance of getting the primers right, and the time saved by automating the primer selection. Also mention other primer design tools that have been inspired by polymarker: \cite{Ma2015}, \cite{Wang2016}
