%!TEX root = ../Main.tex

\chapter{General discussion and final remarks}
This section wraps up by showing the relationship and importance of a comprehensive approach to data analysis, from the field, genetics, molecular biology and genomics. I will also remark how the technology and the resources have changed in the last 4 years. As at the references used at beginning where superseded during the PhD. 


Biology is becoming interdisciplinary

Knowledge from  computer science can be applied to produce software for specific needs, but useful for the comunity

Polyploidy has an extra level of complexity (due to homoeologues), but with the current developments of technology is possible to start getting around them. 

Future project: PolyInDel / . 

In the case of wheat, new resources had been coming out year after year, and each one helps to put everything in to a context. 

With the plethora of information currently available (See section \ref{lit:wheatResourcers}), it is possible to 

Currently, the publicly available wheat resources are scattered as supplemental materials on their correspoinding publication or available as ad hoc systems focused on a particular field.
For example ensembl has two different views for every organism: from the genomic point of view and from the expression data. 
The Collaborative Open Plant Omics (COPO; \citealt{Davey2015}) is trying to integrate different sources and types of data by connecting the data providers. 
This approach requires the cooperation of the service providers, which have their own view of what is important. 
I believe that in order to effectively integrate the resources it is necessary to understand how the users are likely to interact with the data. 

In Chapter \ref{yr15} the integration of different levels of data helped to improve the selection of the candidate SNPs. 
The main criteria for selecting \acrshortpl{snp}  was the\acrshort{bfr} score.
However, thanks to the genetic map from \citet{Wang2014} and the \acrshort{css} scaffolds \citep{Mayer2014}) enabled to confirm that the high scores were in the expected region. 
Currently the wheat reference is improving 

 a better context for the genes should be possible. 
For example, given that


It is more likely to get relevant results in a more effective way using the latest developments. 

